---
title: "WUP_04"
author: "Giulianni P"
date: "fall 2022               "
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
data = read.csv('GSScsv.csv')  
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
 
 We tried to predict WORDSUM based on DEGREE. WORDSUM is a numerical while DEGREE is a Categorical Therefore we'll be using One way Anova due to DEGREES having more than 2 levels.
 
 
# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results



```{r}
boxplot(WORDSUM~DEGREE,data=data)
```

Based on the boxplot above, we can determine that the WORDSUM of that of everything in college is Around the same of eachother, and anything below college falls behind in WORDSUM.

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results

```{r}
favstats(WORDSUM~DEGREE,data=data)
```

The numerical summary shows that the highest average was that of the Graduates while the lowest was Less than highschool.


<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Inferential Results

```{r}
model1 <- aov(WORDSUM~DEGREE,data=data)
summary.aov(model1)
```
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 17, 2, 2))
plot(TukeyHSD(model1),las=2)
```

 Based on the Inferential results The P-Value is .000236 which is less than .005 which helps us determine that we Reject the Null Hypothesis. This shows us that those in highschool-Graduate in less than highschool-Graduate.




<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion
The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

To answer the question stated above, Yes there is a difference between WORDSUM Depending on the DEGREE someone has obtained.



<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
